---
title: "p8105_hw5_zl2746"
author: "Ze Li"
date: "2023-11-08"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
homicide_df = read.csv("data/homicide-data.csv")
```

* Describe the raw data.
  
  There are `r nrow(homicide_df)` observations with `r ncol(homicide_df)` variables in this data set. The variables are `r colnames(homicide_df)`.
  
* Create a city_state variable (e.g. “Baltimore, MD”) and 
* then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide1 = 
  homicide_df |>
  unite(city_state,c(city,state),sep = ', ') |>
  mutate(resolved = as.numeric(disposition == "Closed by arrest"),
         victim_age = as.numeric(victim_age))# |>
  #summarise(n_unsolved = n(resolved == "0"))

```

* For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_df = 
  homicide1 |> 
  filter(city == "Baltimore") #|> 
```


## Problem 2

```{r}

```

